Palaeobiology demo: disparity-through-time and within groups

### 2018-05-13 inst/gitbook/03_specific-tutorials.Rmd
Merge branch 'master' into model-test2
# Conflicts:
#	R/est.VCV.R
#	R/est.mean.R
#	R/input.param.R
#	R/make.dispRity.models.R
#	R/misc.model.test.fun.R
#	R/model.test.R
#	R/model.test.lik.R
#	R/model.test.sim.R
#	R/opt.mode.R
#	man/model.test.Rd
#	tests/testthat/test-model.test.R

```{r}
## Calculating the ellipsoid volume
summary(dispRity(dummy_space, metric = ellipse.volume))
```
> Because there is only one subset (i.e. one matrix) in the dispRity object, this operation is the equivalent of `ellipse.volume(dummy_space)` (with digits).

>>>>

Because there is only one subset (i.e. one matrix) in the dispRity object, the operations below are the equivalent of `metric(dummy_space)` (with rounding).

```{r}
## Calculating the ellipsoid volume
summary(dispRity(dummy_space, metric = ellipse.volume))
```
> WARNING: in such dummy space, this gives the estimation of the ellipsoid volume, not the real ellipsoid volume! See the cautionary note in `?ellipse.volume`.

### 2018-05-13 inst/gitbook/06_palaeo-demo.Rmd
Merge branch 'master' into model-test2
# Conflicts:
#	R/est.VCV.R
#	R/est.mean.R
#	R/input.param.R
#	R/make.dispRity.models.R
#	R/misc.model.test.fun.R
#	R/model.test.R
#	R/model.test.lik.R
#	R/model.test.sim.R
#	R/opt.mode.R
#	man/model.test.Rd
#	tests/testthat/test-model.test.R

This demo aims to give quick overview of the `dispRity` package (v.0.4) for palaeobiology analyses of disparity, including disparity through time analyses.

>>>>

This demo aims to give quick overview of the `dispRity` package (v.`r version_release`) for palaeobiology analyses of disparity, including disparity through time analyses.
